Many claims of group polarization are plausibly false due to inappropriate statistics

### 2022-11-19 GroupPolarizationStatmod/paper/ms.tex
finished refactor FP and t-test tables

% % Author: Matthew Turner

% % \documentclass[11pt,letterpaper]{scrartcl}
% % \documentclass[letterpaper,man,natbib]{apa6}
% \documentclass[11pt,letterpaper]{amsart}
% % \documentclass[11pt, letterpaper]{article}
% % \usepackage{natbib}
% % \documentclass[11pt]{report}
% % \documentclass{report}
% % \documentclass{book}
% \usepackage[bookmarks, hidelinks]{hyperref}
% \usepackage{amssymb,amsmath}
% % \usepackage{fullpage}
% \usepackage{tabulary}
% \usepackage{tabularx}
% \usepackage{float}
% % \usepackage[margin=1.00in]{geometry}
% \usepackage[margin=0.90in]{geometry}

% % \usepackage{fontspec}

% % \usepackage{xunicode}
% % \usepackage{xltxtra}
% % \defaultfontfeatures{Mapping=tex-text}
% % \setmainfont[Ligatures={Common}, Numbers={OldStyle}, Variant=01]{Hoefler Text}
% % \setromanfont[Ligatures={Common}, Numbers={OldStyle}, Variant=01]{Hoefler Text}
% % \setmonofont[Scale=0.95]{PT Sans}
% \usepackage{caption}
% \usepackage{apacite}
% \usepackage{booktabs}
% \usepackage{pslatex}
% \usepackage{subcaption}
% \usepackage{pgfplots}
% \usepackage{wrapfig}
% \usepackage[english]{babel}
% \usepackage{lmodern}
% % \doublespace
% % \usepackage{url}
% \usepackage{bigfoot}
% \usepackage[export]{adjustbox}
% % \setlength\intextsep{0pt}

% \usepackage{graphicx}

\documentclass[12pt, letterpaper]{article}
\usepackage{fontspec} 
\usepackage{marvosym}
\usepackage{setspace}
\usepackage{longtable}
% DOCUMENT LAYOUT
% \usepackage{geometry} 
\usepackage[margin=0.90in]{geometry}
\usepackage{lineno}
\usepackage[usenames,dvipsnames]{xcolor}
% \geometry{letterpaper, textwidth=5.5in, textheight=8.5in, marginparsep=7pt, marginparwidth=.6in}
% \setlength\parindent{0in}

@@

% \renewcommand{\thesubsection}{\arabic{subsection}.}
% FONTS
% \usepackage[usenames,dvipsnames]{color}
% \usepackage{xunicode}
% \usepackage{xltxtra}
\defaultfontfeatures{Mapping=tex-text}
% \setromanfont[Ligatures={Common}, Variant=01]{Hoefler Text}
% \setromanfont[Ligatures={Common}, Variant=01]{Palatino}
\setromanfont[Ligatures={Common}, Variant=01]{Baskerville}
% \setromanfont[Ligatures={Common}, Variant=01]{Plantagenet Cherokee}
% \setmainfont [BoldFont={STIX Two Text SemiBold}, Ligatures={Common},
% Numbers={OldStyle}, Variant=01]{STIX Two Text}
% \setmainfont [BoldFont={STIX Two Text SemiBold}, Ligatures={Common},
% Numbers={OldStyle}, Variant=01]{STIX Two Text}
% \setromanfont [Ligatures={Common},
% Numbers={OldStyle}, Variant=01]{STIX Two Text}
\setmonofont[Scale=0.95]{PT Sans}

% ---- CUSTOM COMMANDS
% \chardef\&="E050
\newcommand{\html}[1]{\href{#1}{\scriptsize\textsc{[html]}}}
\newcommand{\pdf}[1]{\href{#1}{\scriptsize\textsc{[pdf]}}}
\newcommand{\doi}[1]{\href{#1}{\scriptsize\textsc{[doi]}}}
\newcommand{\lurl}[1]{\href{#1}{\scriptsize\textsc{[link]}}}

\newcommand{\githubsymbol}{\raisebox{-2pt}{\includegraphics[height=10.5pt]{github}}}
\newcommand{\twittersymbol}{\raisebox{-2pt}{\includegraphics[height=10.5pt]{twitter}}}
\newcommand{\monitorsymbol}{\raisebox{-2pt}{\includegraphics[height=10.5pt]{monitor}}}

% ---- MARGIN YEARS
\usepackage{marginnote}
\newcommand{\amper{}}{\chardef\amper="E0BD }
\newcommand{\years}[1]{\marginnote{\small #1}}
\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{7pt}
\reversemarginpar

@@

% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR
\usepackage[%dvipdfm, 
bookmarks, colorlinks, breaklinks, 
% ---- FILL IN HERE THE TITLE AND AUTHOR
	pdftitle={Matthew A. Turner - Vita},
	pdfauthor={Matthew A. Turner, PhD},
	pdfproducer={https://mt.digital}
]{hyperref}  
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=MidnightBlue}

@@

\title{Group polarization is often a mirage caused by inappropriate statistical analyses}
% \shorttitle{Group polarization or simple consensus?}
\author[1,2]{{Matthew A.~Turner}}
\affil[1]{Department of Earth System Science, Stanford University}
\affil[2]{Division of Social Sciences, Stanford Doerr School of Sustainability, Stanford University}

@@

@@

\spacing{1.0}
\input{plausibleFP-table.tex}
\spacing{1.5}

>>>>

\documentclass[11pt, letterpaper]{article}
\usepackage{marvosym}
\usepackage{setspace}
\usepackage{longtable}
% DOCUMENT LAYOUT
% \usepackage{geometry} 
\usepackage[margin=1.0in]{geometry}
\usepackage{lineno}
\usepackage[usenames,dvipsnames]{xcolor}
% \geometry{letterpaper, textwidth=5.5in, textheight=8.5in, marginparsep=7pt, marginparwidth=.6in}
% \setlength\parindent{0in}

@@

% \usepackage{fontspec} 
% \renewcommand{\thesubsection}{\arabic{subsection}.}
% FONTS
% \usepackage[usenames,dvipsnames]{color}
% \usepackage{xunicode}
% \usepackage{xltxtra}
% \defaultfontfeatures{Mapping=tex-text}
% % \setromanfont[Ligatures={Common}, Variant=01]{Hoefler Text}
% % \setromanfont[Ligatures={Common}, Variant=01]{Palatino}
% \setromanfont[Ligatures={Common}, Variant=01]{Baskerville}
% % \setromanfont[Ligatures={Common}, Variant=01]{STIX Two Math}
% % \setmathrm{Baskerville}
% % \setromanfont[Ligatures={Common}, Variant=01]{Plantagenet Cherokee}
% % \setmainfont [BoldFont={STIX Two Text SemiBold}, Ligatures={Common},
% % Numbers={OldStyle}, Variant=01]{STIX Two Math}
% % \setmathrm{STIX Two Math}
% % \setmainfont [BoldFont={STIX Two Text SemiBold}, Ligatures={Common},
% % Numbers={OldStyle}, Variant=01]{STIX Two Text}
% % \setromanfont [Ligatures={Common},
% % Numbers={OldStyle}, Variant=01]{STIX Two Text}
% \setmonofont[Scale=0.95]{PT Sans}

\usepackage{mathspec}
% \setallmainfonts(Digits,Latin){STIX Two Text}
% \setallmainfonts(Digits,Latin){Baskerville}
% \setallmainfonts(Digits,Latin){Plantagenet Cherokee}
\setallmainfonts(Digits,Latin){Palatino}
% \setallmainfonts(Digits,Latin){Hoefler Text}

@@

% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR
\usepackage[%dvipdfm, 
bookmarks, colorlinks, breaklinks, 
% ---- FILL IN HERE THE TITLE AND AUTHOR
	pdftitle={Many claims of group polarization are plausibly false due to inappropriate
    statistics},
	pdfauthor={Matthew A. Turner},
	pdfproducer={https://mt.digital}
]{hyperref}  
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=MidnightBlue}

@@

\title{Many claims of group polarization are plausibly false due to inappropriate
    statistics}
% \shorttitle{Group polarization or simple consensus?}
\author[1,2]{{Matthew A.~Turner}}
\affil[1]{Department of Earth System Science, Stanford University}
\affil[2]{Division of Social Sciences, Stanford Doerr School of Sustainability, Stanford University}

@@

\begin{equation}
  \int_{-\infty}^\infty x^2 dx \neq \pi
\end{equation}
\noindent

@@

\vspace{.5em}
\spacing{1.0}
% \input{plausibleFP-table.tex}
  \begin{table}
    \begin{center}
      \caption{Number and fraction of experimental conditions where group polarization was
               reported to have occurred, but plausibly did not.}
      \vspace{.5em}
      \input{plausibleFP-table-custom.tex}
    \end{center}
  \end{table}
\spacing{1.5}
